OSF management

### 2021-01-05 osf/comps/data/README.Rmd
update osf/manage-osf.Rmd to reflect restructuring in OSF repo: take 2

---
title: "Dataset & Materials"
output:
  github_document:
    html_preview: false
---

@@

This directory contains 2 subdirectories: `exp-materials/` and `data/`.

Files and results of the norming study are in `exp-materials/`
The `data` directory hosts the `.wav` and `.TextGrid` files from the production experiment.
See the `README.md` files of each individual directory for more information about the contents.

>>>>

---
title: "Data component"
output:
  github_document:
    html_preview: false
---

@@

This component hosts the data of the *Many Speech Analyses* project.
For an overview, see the [wiki](https://osf.io/rdtx5/wiki/home/).

There are 2 subdirectories:

- The `norming/` directory holds the files of the norming study.
- The `production/` directory contains the `.wav` and `.TextGrid` files from the production experiment.

See the `README.md` files of each individual directory for more information about the contents.

### 2021-01-05 osf/comps/data/production/audio/README.Rmd
update osf/manage-osf.Rmd to reflect restructuring in OSF repo: take 2

---
title: "Data"
output:
  github_document:
    html_preview: false
---

@@

This directory contains the files from the production experiment:

@@

```{r data_files, include=FALSE}
osf_ls_files(data_comp, "data") %>%
  select(name) %>%
  filter(str_detect(name, ".*\\.md", negate = TRUE)) %>%
  arrange(name)
```

>>>>

---
title: "Audio and annotation files of the production study"
output:
  github_document:
    html_preview: false
---

@@

This directory contains the files from the production study:

@@

```{r data_files, include=FALSE}
osf_ls_files(data_comp, "production/audio") %>%
  select(name) %>%
  filter(str_detect(name, ".*\\.md", negate = TRUE)) %>%
  arrange(name)
```

### 2021-01-05 osf/comps/data/production/trial-lists/README.Rmd
update osf/manage-osf.Rmd to reflect restructuring in OSF repo: take 2

---
title: "Production experiment"
output:
  github_document:
    html_preview: false
---

@@

```{r data_files, include=FALSE}
osf_ls_files(data_comp, "exp-materials/experiment") %>%
  select(name) %>%
  filter(str_detect(name, ".*\\.md", negate = TRUE)) %>%
  arrange(name)
```

>>>>

---
title: "Trial lists of the production study"
output:
  github_document:
    html_preview: false
---

@@

```{r data_files, include=FALSE}
osf_ls_files(data_comp, "production/trial-lists") %>%
  select(name) %>%
  filter(str_detect(name, ".*\\.md", negate = TRUE)) %>%
  arrange(name)
```

### 2021-01-05 osf/manage-osf.Rmd
update osf/manage-osf.Rmd to reflect restructuring in OSF repo: take 2

# data/data
raw <- data_comp_files %>% filter(name == "data")

osf_rm(osf_ls_files(data_comp, "data", pattern = "README.md"), check = FALSE)
osf_upload(raw, path = "./osf/comps/data/data/README.md", conflicts = "overwrite", verbose = T)

# data/exp-materials
materials <- data_comp_files %>% filter(name == "exp-materials")

osf_rm(osf_ls_files(data_comp, "exp-materials", pattern = "README.md"), check = FALSE)
osf_upload(materials, path = "./osf/comps/data/exp-materials/README.md", conflicts = "overwrite", verbose = T)

# data/exp-materials/norming
osf_rm(osf_ls_files(data_comp, "exp-materials/norming", pattern = "README.md"), check = FALSE)
osf_upload(osf_ls_files(data_comp, "exp-materials", pattern = "norming"), path = "./osf/comps/data/exp-materials/norming/README.md", conflicts = "overwrite", verbose = T)

# data/exp-materials/experiment
osf_rm(osf_ls_files(data_comp, "exp-materials/experiment", pattern = "README.md"), check = FALSE)
osf_upload(osf_ls_files(data_comp, "exp-materials", pattern = "experiment"), path = "./osf/comps/data/exp-materials/experiment/README.md", conflicts = "overwrite", verbose = T)
```

>>>>

# data/norming/
raw <- data_comp_files %>% filter(name == "norming")

#### delete old readme ("overwrite" option fails)
old_readme <- osf_ls_files(data_comp, "norming", pattern = "README.md")
osf_rm(old_readme, check = FALSE)

#### upload new readme
osf_upload(
  raw,
  path = "./osf/comps/data/norming/README.md",
  conflicts = "overwrite", verbose = T)

# data/production/audio/
#### delete old readme
old_readme <- osf_ls_files(data_comp, "production/audio", pattern = "README.md")
osf_rm(old_readme, check = FALSE)

#### upload new readme
audio <- osf_ls_files(data_comp, "production", pattern = "audio")
osf_upload(
  audio,
  path = "./osf/comps/data/production/audio/README.md",
  conflicts = "overwrite", verbose = T)

# data/production/trial-lists
#### delete old readme
old_readme <- osf_ls_files(data_comp, "production/trial-lists", pattern = "README.md")
osf_rm(old_readme, check = FALSE)

#### upload new readme
trials <- osf_ls_files(data_comp, "production", pattern = "trial-lists")
osf_upload(
  trials,
  path = "./osf/comps/data/production/trial-lists/README.md",
  conflicts = "overwrite", verbose = T)
```
